Reproducible Research in R: A Tutorial on how to Do the Same Thing More Than Once

### 2021-11-16 manuscript.Rmd
where is the line? closes #272
the sentence before makes it clear already closes #264

With this paper, we pursue two aims.
First, we want to introduce researchers to a notion of automated reproducibility that requires no manual steps, apart from the initial setup of the software environment. 
Secondly, we discuss the possibilities that such automated reproducibility offers to improve not only the way research results are created and recovered, but also how this may change the general approach to a research project.
With regard to the first goal, we show how to address four common threats to reproducibility with tools originating from software engineering [see @Peikert2019 for details].
Then we present a tutorial on how to employ these tools to achieve automated reproducibility.
A single tutorial cannot comprehensively introduce the reader to the individual tools, but this tutorial is intended to help readers to build a coherent workflow.
It is aimed at researchers who regularly write code to analyze their data and are willing to make relevant code, data, and materials available, either publicly or on request.
Ideally, our reader has already created a dynamic document at some point in time (e.g., with R Markdown or Jupyter) and attempted to track a file with version control (e.g., with Git). 
The R package `repro` supports researchers in setting up the required software and in adopting this workflow.
We present automated reproducibility as best practice, a goal that is not always achieved due to limited resources, technical restrictions, or practical considerations, but is very much worth striving for.
If some parts of the workflow prove to be unfeasible, we encourage the reader to find their own solutions and to concentrate on the feasible parts.

@@

If simulating data proves to be too challenging, researchers can delay their preregistration until they have gathered data and repurpose the empirical data.
In doing so, the researchers must walk a fine but important line.
Of course, they must not analyze the data before they write the preregistration.
Nevertheless, they may obfuscate the real data (before actually looking at them) by shuffling the order of rows for each variable (independently of each other) in cross-sectional data or otherwise by creating synthetic data that allow them to test the function `planned_analysis()` without actually revealing the observed research outcomes.
Preregistration after data collection is common for secondary data analysis of data obtained by other research groups [@westonRecommendationsIncreasingTransparency2019] but not so much within the same research project.
We argue that it is still an eligible preregistration.
In fact, guidelines for clinical trials also recommend analysis of blinded data  to test the practicality of the preregistration [@ICH1998].
Since the data is obfuscated, virtually no information is revealed to the researchers, and they can not employ their degrees of freedom effectively to influence the results (see section above).
Shuffling leaves only univariate information, so this procedure is only applicable for bi- or multivariate hypotheses.
The researcher can still access the information about means or proportions (e.g., the number of participants belonging to group "A" are in the dataset), but are unbiased for all relations between variables (e.g., members of group "A" have a greater mean in variable "Z").
To be clear, any exploration of the data before preregistration (PAC or otherwise) renders the preregistration invalid and amounts to (albeit sometimes unintentional) scientific misconduct.

>>>>

With this paper, we pursue two aims.
First, we want to introduce researchers to a notion of automated reproducibility that requires no manual steps, apart from the initial setup of the software environment. 
Secondly, we discuss the possibilities that such automated reproducibility offers to improve not only the way research results are created and recovered, but also how this may change the general approach to a research project.
With regard to the first goal, we show how to address four common threats to reproducibility with tools originating from software engineering [see @Peikert2019 for details].
Then we present a tutorial on how to employ these tools to achieve automated reproducibility.
A single tutorial cannot comprehensively introduce the reader to the individual tools, but this tutorial is intended to help readers to build a coherent workflow.
It is aimed at researchers who regularly write code to analyze their data and are willing to make relevant code, data, and materials available, either publicly or on request.
Ideally, our reader has already created a dynamic document at some point in time (e.g., with R Markdown or Jupyter) and attempted to track a file with version control (e.g., with Git). 
The R package `repro` supports researchers in setting up the required software and in adopting this workflow.
We present automated reproducibility as best practice, a goal that is not always achieved due to limited resources, technical restrictions, or practical considerations, but is very much worth striving for.

@@

If simulating data proves to be too challenging, researchers can delay their preregistration until they have gathered data and repurpose the empirical data.
In doing so, the researchers must walk a fine but important line.
Of course, they must not analyze the data before they write the preregistration.
Nevertheless, they may obfuscate the real data (before actually looking at them) by shuffling the order of rows for each variable (independently of each other) in cross-sectional data or otherwise by creating synthetic data that allow them to test the function `planned_analysis()` without actually revealing the observed research outcomes.
Preregistration after data collection is common for secondary data analysis of data obtained by other research groups [@westonRecommendationsIncreasingTransparency2019] but not so much within the same research project.
We argue that it is still an eligible preregistration.
In fact, guidelines for clinical trials also recommend analysis of blinded data  to test the practicality of the preregistration [@ICH1998].
Since the data is obfuscated, virtually no information is revealed to the researchers, and they can not employ their degrees of freedom effectively to influence the results (see section above).
Shuffling leaves only univariate information, so this procedure is only applicable for bi- or multivariate hypotheses.
The researcher can still access the information about means or proportions (e.g., the number of participants belonging to group "A" are in the dataset), but are unbiased for all relations between variables (e.g., members of group "A" have a greater mean in variable "Z").
To be clear, any exploration of the data before preregistration (PAC or otherwise) renders the preregistration invalid and amounts to (albeit sometimes unintentional) scientific misconduct.
The aim is transparency and the line that shall not be crossed is learning about the research outcomes, but what this means differs for each research project.
